---
title: "Prepare network and user data"
author: "Lowson Li"
output:
  html_notebook:
    code_folding: show
    highlight: tango
    number_sections: yes
    theme: simplex
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Load packages
```{r}
library(tidyverse)
library(igraph)
library(visNetwork)
library(spdep)
library(spatialreg)
library(igraph)
library(ade4)
```

# Neo4j

Dev version from GitHub
```{r echo=TRUE}
# remotes::install_github("neo4j-rstats/neo4r")
```
## Connection 

Create connection 
```{r echo=TRUE}
library(neo4r)
con <- neo4j_api$new(
  url = "http://localhost:7474",
  user = "neo4j", 
  password = "neo4j"
  )
```

Check connection 
```{r}
con$ping()
```
```{r}
con$get_version()
```
```{r}
con$get_constraints()
```
```{r}
con$get_labels()
```
```{r}
con$get_relationships()
```

```{r}
con$get_index()
```

## Retrieve data from the API

Unnest node 
```{r}
res <- 'MATCH (u:User)-[:WROTE]->(r:Review)-[:REVIEWS]->(b:Business)-[:IN_CATEGORY]->(c:Category) 
	WHERE b.state = "AZ" AND b.is_open = 1 AND b.city ="Phoenix" AND c.id CONTAINS "Restaurant" 
	WITH u MATCH (u)-[:FRIEND*0..1]-(n) WHERE n.name IS NOT NULL AND n.id <> "None" 
	RETURN DISTINCT u  LIMIT 10' %>%
  call_neo4j(con, type = "graph")
unnest_nodes(res$nodes)
```

Unnest graph
```{r echo=TRUE}
res <- 'MATCH (u:User)-[:WROTE]->(r:Review)-[:REVIEWS]->(b:Business)-[:IN_CATEGORY]->(c:Category) 
	WHERE b.state = "AZ" AND b.is_open = 1 AND b.city ="Phoenix" AND c.id CONTAINS "Restaurant" 
	WITH u MATCH (u:User)-[f]-(n:User) WHERE u.name IS NOT NULL AND u.id <> "None" AND n.name IS NOT NULL AND n.id <> "None"
	RETURN DISTINCT u,Type(f),f,n limit 100' %>%
  call_neo4j(con, type = "graph") %>%
  unnest_graph()
```
```{r}
res$nodes
```

```{r}
res$relationships
```

Extract with `path`

```{r echo=TRUE}
res <- 'MATCH (u:User)-[:WROTE]->(r:Review)-[:REVIEWS]->(b:Business)-[:IN_CATEGORY]->(c:Category) 
WHERE b.state = "AZ" AND b.is_open = 1 AND b.city ="Phoenix" AND c.id CONTAINS "Restaurant" 
WITH u 
MATCH p=(u:User)-[f]->(n:User) 
WHERE u.name IS NOT NULL AND u.id <> "None" AND n.name IS NOT NULL AND n.id <> "None"
RETURN DISTINCT p LIMIT 100' %>%
  call_neo4j(con, type = "graph") %>%
  unnest_graph()
```

## Convert to igraph 

Prepare nodes
```{r echo=TRUE}
res$nodes <-
  res$nodes %>%
  select(id, label = value, everything())
``` 

Prepare relationships
```{r echo=TRUE}
res$relationships <- res$relationships %>%
  select(startNode, endNode, type, everything())
```

Save network in igraph
```{r echo=TRUE}
graph_object <- igraph::graph_from_data_frame(
  d = res$relationships, 
  directed = FALSE, 
  vertices = res$nodes
)
```

## Export nodes & relationships from neo4j

Cypher - export users nodes 

```{Cypher}
WITH "MATCH (u:User)-[:WROTE]->(:Review)-[:REVIEWS]->(b:Business)-[:IN_CATEGORY]->(c:Category) 
WHERE b.is_open =1 AND b.state = 'AZ' AND c.id CONTAINS 'Restaurant' AND b.city = 'Phoenix' AND b.is_open = 1
WITH u
MATCH (u)-[:FRIEND*0..1]-(f)
WHERE u.name IS NOT NULL AND u.id <> 'None' AND f.name IS NOT NULL AND f.id <>'None'
WITH DISTINCT f
RETURN id(f) as neo_id, f.id as user_id" AS query
CALL apoc.export.csv.query(query, "node.csv", {})
YIELD file, source, format, nodes, relationships, properties, time, rows, batchSize, batches, done, data
RETURN file, source, format, nodes, relationships, properties, time, rows, batchSize, batches, done, data;
```

Cypher - export relationships 

```{Cypher}
WITH "MATCH (u:User)-[:WROTE]->(:Review)-[:REVIEWS]->(b:Business)-[:IN_CATEGORY]->(c:Category) 
WHERE b.is_open =1 AND b.state = 'AZ' AND c.id CONTAINS 'Restaurant' AND b.city = 'Phoenix' AND b.is_open = 1
WITH u
MATCH p=(u)-[:FRIEND]-(f)
WHERE u.name IS NOT NULL AND u.id <> 'None' AND f.name IS NOT NULL AND f.id <>'None'
WITH DISTINCT p
UNWIND apoc.coll.pairsMin(nodes(p)) as pair
RETURN id(pair[0]) as from, id(pair[1]) as to" AS query
CALL apoc.export.csv.query(query, "friendship2.csv", {})
YIELD file, source, format, nodes, relationships, properties, time, rows, batchSize, batches, done, data
RETURN file, source, format, nodes, relationships, properties, time, rows, batchSize, batches, done, data;
```

## Strategy 
 
Since the file is too large for directed import to `igraph` object via `neo4r`, I decide to **export**:

1) node list
2) relationship list 

After getting these 2 critical information, I can create `igraph` object.


from `neo4j` **directly**. 

I will run **community detection algoritm** on `neo4j` first, then save the **node** and **relationship** on the server.
Then load it from `Dremio`, use the `user_id` to join other nodes attributes.

## Node check 

Import nodes 
```{r}
library(readr)
node <- read_csv("~/neo4j-community-3.5.15/import/node_lv.csv")
```

Check for distinct node 
```{r}
node %>% 
  distinct(neo_id) %>% 
  nrow()
```


## Relationship check

Load the distinct path version of relationship
```{r}
library(readr)
friendship_lv <- read_csv("~/neo4j-community-3.5.15/import/friendship_lv.csv")
```

Count all path
```{r}
friendship_lv %>%
  nrow()
```



Count distinct start node
```{r}
friendship_lv %>%
  distinct(from) %>%
  nrow()
```

Count distinct end node
```{r}
friendship_lv %>%
  distinct(to) %>%
  nrow()
```

Count distinct path
```{r}
friendship_lv%>%
  distinct(from, to) %>%
  nrow()
```

Check the duplicated path 

## Test igraph object
```{r echo=TRUE}
graph_object <- igraph::graph_from_data_frame(
  d = friendship_lv, 
  directed = FALSE, 
  vertices = node
)
```

Check if the graph is simple(no multiple vertex between 2 nodes)


```{r}
is_simple(graph_object)
```

```{r echo=TRUE}
graph_simp <- simplify(graph_object)
```


# Network descriptives
## Density
The proportion of present edges from all possible edges in the network.
```{r}
edge_density(graph_simp, loops=F)
```

## Transitivity

* global - ratio of triangles (direction disregarded) to connected triples.
* local - ratio of triangles to connected triples each vertex is part of.

```{r}
transitivity(graph_simp, type="global")  # net is treated as an undirected network

# transitivity(as.undirected(graph_simp, mode="collapse")) # same as above

# transitivity(net, type="local")

# triad_census(net) # for directed networks 
```

## Diameter
A network diameter is the longest geodesic distance (length of the shortest path between two nodes) in the network. In `igraph`, `diameter()` returns the distance, while `get_diameter()` returns the nodes along the first found path of that distance.

Note that edge weights are used by default, unless set to NA.
```{r}
# diameter(graph_object, directed=F, weights=NA)
# slow, do not run
```

## Degrees
The function `degree()` has a mode of `in` for in-degree, `out` for out-degree, and `all` or total for total degree.

Degree distribution 
```{r}
deg <- degree(graph_simp, mode="all")

deg <- deg %>% 
  table() %>% 
  as.data.frame()

deg <- deg %>%
  mutate(degrees = as.numeric(`.`)) %>%
  select(-`.`)

ggplot(deg, aes(x = degrees, y = Freq)) +
  geom_point() +
  scale_x_continuous("Degree\n(nodes with this amount of connections)",
                     #breaks = c(1, 3, 10, 30, 100, 300),
                     trans = "log10") +
  scale_y_continuous("Frequency\n(how many of them)",
                     #breaks = c(1, 3, 10, 30, 100, 300, 1000),
                     trans = "log10") +
  ggtitle("Degree Distribution (log-log)") +
  theme_bw()
```


## Assortativity
```{r}
assortativity_degree(graph_simp, directed=F)
```


# Community detection (TBC)
## Newman-Girvan
Community detection based on edge betweenness.
High-betweenness edges are removed sequentially (recalculating at each step) and the best partitioning of the network is selected.
```{r}
# ceb <- cluster_edge_betweenness(grgraph_object) 
# slow, do not run 
```

Community detection based on greedy optimization of modularity
```{r}
# cfg <- cluster_fast_greedy(graph_object)
```
```{r}
# cfg <-
#   simplify(graph_object) %>%
#   cluster_fast_greedy()
```

# Dremio data 

Link id of selected nodes to their atributes.
```{r}
dremio_host <- "localhost"
dremio_port <- "31010"
dremio_uid <- "Lowson"
dremio_pwd <- "R08323023"

con <- DBI::dbConnect(odbc::odbc(),
  driver = "Dremio ODBC Driver 64-bit",
  uid = dremio_uid,
  pwd = dremio_pwd,
  host = dremio_host,
  port = dremio_port,
  AuthenticationType = "Basic Authentication", ConnectionType = "Direct"
)

community_lv_full <- con %>% tbl(sql("SELECT * FROM community_lv_full"))
```

Note that the file is failed to load, which is similar to the the preview issue of the Dremio.

Laod after download the `csv` file from Dremio

```{r}
library(readr)
community_lv_full <- read_csv("../Data/community_lv_full.csv")
# View(community_lv_full)
```

Skim data 
```{r}
skimr::skim(community_lv_full) %>% knitr::kable()
```







# Reference 

[Using R & Neo4J](https://neo4j-rstats.github.io/user-guide/)
[Network and node descriptives](https://kateto.net/netscix2016.html)
[](https://community.neo4j.com/t/access-nodes-in-path/6764)
[](https://community.neo4j.com/t/how-to-return-from-to-nodes-from-a-path/6876)
[](https://igraph.org/r/doc/simplify.html)
[Using Dremio with R and dplyr on macOS](https://cojamalo.github.io/macOS_Dremio_R/guide.html#download-and-install-dremio-odbc-driver)
